---
title: "Music Insights"
author: "Jerusalem Moore"
output:
  html_document:
    df_print: paged
---

First, we need to use tidyverse to handle data importing and wrangling...

```{r}
install.packages("tidyverse", repos = "http://cran.us.r-project.org")
library("tidyverse")

survey <- read_csv("https://raw.githubusercontent.com/introdsci/MusicSurvey/master/music-survey.csv")
preferences <- read_csv("https://raw.githubusercontent.com/introdsci/MusicSurvey/master/preferences-survey.csv")
```

Cleaning column names

```{r}
colnames(survey)[colnames(survey) == "First, we are going to create a pseudonym for you to keep this survey anonymous (more or less). Which pseudonym generator would you prefer?"] <- "generator_name"

```
There are variables with redundant values
Survey column "which musical instrument/talents do you play?" formatting is undefined and takes free variables which has to be cleaned

?strsplit may help

There are also some helpful parse functions we can use
```{r}
parse_datetime
```
We would like to present the column names in a more consistent and streamlined manner.
```{r}
colnames(survey)
```

```{r}
colnames(survey)[colnames(survey) == "Timestamp"] <- "Time_Submitted"
colnames(survey)[colnames(survey) == "generator_name"] <- "pseudonym_generator"
colnames(survey)[colnames(survey) == "What is your pseudonym?"] <- "pseudonym"
colnames(survey)[colnames(survey) == "Sex"] <- "sex"
colnames(survey)[colnames(survey) == "Major"] <- "academic_major"
colnames(survey)[colnames(survey) == "Academic Year"] <- "academic_level"
colnames(survey)[colnames(survey) == "Year you were born (YYYY)"] <- "year_born"
colnames(survey)[colnames(survey) == "Which musical instruments/talents do you play? (Select all that apply)"] <- "instrument_list"
colnames(survey)[colnames(survey) == "Artist"] <- "favorite_song_artist"
colnames(survey)[colnames(survey) == "Song"] <- "favorite_song"
colnames(survey)[colnames(survey) == "Link to song (on Youtube or Vimeo)"] <- "favorite_song_link"
```

We are going to use some tidyverse features(i.e. dplyr and tidyr)

```{r}
library(dplyr)
library(tidyr)
```

Using the previously downloaded tidyverse features, we can build some data tables. We'll start by making a "person" table and then a "favorite_song" table.

```{r}
person <- tibble(pseudonym = survey$pseudonym, pseudonym_generator = survey$pseudonym_generator, sex = survey$sex, academic_major = survey$academic_major, academic_level = survey$academic_level, year_born = survey$year_born, Time_Submitted = survey$Time_Submitted)

favorite_song <- tibble(favorite_song_artist = survey$favorite_song_artist, favorite_song = survey$favorite_song, favorite_song_link = survey$favorite_song_link, pseudonym = survey$pseudonym)
```

Date format manipulation using "readr" and "parse_datetime"

```{r}
survey$Time_Submitted <- as.POSIXlt(parse_datetime(survey$Time_Submitted, format = "%m/%d/%y %H:%M"))
```

We will organize preferences and use it to create a "ratings" table

```{r}
ratings <- tibble(pseudonym = preferences$pseudonym, artist_song = preferences$artist_song, ratings = preferences$ratings)
```